### 2020-03-18 thesis/pretext.tex
went through the pretext again.

\justify{}
\doublespacing
This work introduces the development of the novel flat-histogram Monte
Carlo (MC) method SAD and explores the convergence properties of a
variety of related weight-based MC methods. The new method is applied
to a variety of physical ‘test’ systems including the 2D Ising model,
square-well fluid, and Lennard-Jones clusters. A driving motivation for
developing novel Monte Carlo methods that have physically based tunable
parameters is to provide simulation methods for exploring metal-organic
frameworks (MOFs). A theoretical framework for gas adsorption and
delivery in metal-organic frameworks is developed and compared with
experimental data. SAD is introduced as a powerful method for examining
thermodynamic properties for MOFs. A preliminary groundwork is laid for
the future development of a multi-dimensional SAD which would be able
to compute all isotherms for any given MOF thereby providing a powerful
way for researchers to determine a MOF’s suitability for gas storage
applications.

@@

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	ACKNOWLEDGEMENTS
\end{center}
\justify{}
\doublespacing
I gratefully acknowledge my graduate advisor David Roundy for his
constant support and guidance throughout my research. His breadth of knowledge
and hands-off approach have tremendously helped me to develop as a scientific
researcher.
I express thanks to my graduate committee members: David McIntyre, Davide Lazzati, Yun-Shik Lee, and GCR Chih-hung (Alex) Chang.
I would like to acknowledge the many outstanding graduate students that have positively impacted me (too many to name here but you know who you are).
I would like to acknowledge some of the outstanding undergraduate students
from our research lab that have worked on related research:
Tanner Simpson, Cade Trotter, and Christopher May.
Thank you all for your helpful discussions related to research and life in
general.
Finally, I would like to thank my parents for their unconditional support
throughout my PhD research.

>>>>

\justify{}
\doublespacing
This work introduces the novel flat-histogram Monte
Carlo (MC) method SAD and explores the convergence properties of a
variety of related weight-based MC methods. The new method is applied
to a variety of physical ‘test’ systems including the 2D Ising model,
square-well fluid, and a Lennard-Jones cluster. A driving motivation for
developing novel Monte Carlo methods that have physically based tunable
parameters is to provide simulation methods for exploring metal-organic
frameworks (MOFs). A theoretical framework for gas adsorption and
delivery in metal-organic frameworks is developed and compared with
experimental data. SAD is introduced as a powerful method for examining
thermodynamic properties for MOFs. A preliminary groundwork is laid for
the future development of a multi-dimensional SAD which would be able
to compute all properties of interest for any given MOF thereby providing a powerful way for researchers to determine a MOF’s suitability for gas storage
applications.

@@

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	ACKNOWLEDGEMENTS
\end{center}
\justify{}
\doublespacing
I gratefully acknowledge my graduate advisor David Roundy for his
constant support and guidance throughout my research. His breadth of knowledge
and hands-off advising have tremendously helped me to develop as an independent scientific researcher. I express thanks to my graduate committee members: David McIntyre, Davide Lazzati, Yun-Shik Lee, and GCR Chih-hung (Alex) Chang.
I would like to acknowledge the many outstanding graduate students that have positively impacted me personally and professionally (too many to name here but you know who you are). I would like to acknowledge some of the outstanding undergraduate students from our research lab that have worked on related research: Tanner Simpson, Cade Trotter, and Christopher May. Thank you all for your helpful discussions related to research and life in general. Finally, I would like to thank my parents for their unconditional support throughout my PhD research.
